\documentclass[letterpaper,11pt]{article}
\usepackage{fancyhdr}
\usepackage[pdftex]{hyperref}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item[]
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \small#3 & \small #4 \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}
\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{Hamza MOUHIB} &  \href{mailto:d4wan5564x@gmail.com}{d4wan5564x@gmail.com}\\
  \textbf{Software Developer} & \href{tel:+212694538355}{+212 694 53 83 55} \\
  \textbf{} & \href{https://github.com/iTsLhaj}{iTsLhaj@github.com} \\
  \textbf{} & \href{https://ma.linkedin.com/in/hamza-mouhib-861776252/}{hamza-mouhib@linkedin.com} 
\end{tabular*}

%-----------PROJECTS-----------------
\section{Projects}
\resumeSubHeadingListStart

\resumeSubheading
      {\href{https://github.com/iTsLhaj/ft_transcendence}{FT\_Transcendence (Flask, Node.js, TypeScript, Prisma, SQLite)}}{Aug 2025 - Oct 2025}
      {Team Project}{}
      \resumeItemListStart
        \resumeItem{Full-Stack Web Application}
          {Contributed to a multiplayer Pong web application featuring user authentication, friend management, and real-time chat using \textbf{Flask} and \textbf{Node.js} with \textbf{TypeScript}.}
        \resumeItem{Backend Development \& Leadership}
          {Led the backend development, splitting tasks, managing GitHub workflow, and ensuring smooth collaboration with the frontend team.}
        \resumeItem{Database Management}
          {Modeled and managed data for users, friends, matches, and chat messages using \textbf{Prisma ORM} with \textbf{SQLite}.}
        \resumeItem{Authentication \& Security}
          {Implemented secure user authentication system, including session handling, OAuth2 support, and two-factor authentication (2FA).}
        \resumeItem{Team Collaboration}
          {Worked closely with team members to integrate backend services with frontend, maintaining code quality and project organization.}
      \resumeItemListEnd

\resumeSubheading 
{\href{https://github.com/iTsLhaj/inception-42}{Inception (Docker, Makefile, Docker Compose,
Bash scripting)}}{June 2025 - July 2025}
{Solo Project}{}
\resumeItemListStart
  \resumeItem{Containerization with Docker}
    {Containerized the application using Docker, ensuring a consistent and reproducible environment for development, testing, and deployment across different systems.}
  \resumeItem{Docker Compose}
    {Utilized Docker Compose to manage multi-container applications, simplifying the orchestration of different services and ensuring seamless communication between containers.}
  \resumeItem{Automation with Bash Scripts}
    {Developed Bash scripts to automate container setup, configuration, and deployment tasks, improving productivity and reducing manual errors.}
\resumeItemListEnd

\resumeSubheading
{\href{https://github.com/iTsLhaj/webserv}{HTTP WebServer (C++, Makefile)}}{Jan 2025 - April 2025}
{Team Project}{}
\resumeItemListStart
  \resumeItem{HTTP Request Parsing}
    {Implemented full HTTP request parsing, including headers, methods (GET, POST, etc.), and body content, ensuring accurate request handling for the server.}
  \resumeItem{Configuration File Parsing}
    {Developed a parser for the server configuration file with syntax similar to Nginx, enabling flexible and dynamic server setup.}
  \resumeItem{Session Management}
    {Handled sessions and state tracking, allowing persistent user data across multiple requests and improving server functionality.}
  \resumeItem{CGI Scripting}
    {Wrote CGI scripts in Python and Bash to generate dynamic content in response to client requests.}
  \resumeItem{Networking Fundamentals}
    {Gained practical experience with sockets and basic network programming in C/C++, enhancing understanding of low-level server operations.}
\resumeItemListEnd

\resumeSubHeadingListEnd

%-----------Education-----------------
\section{Education}
\resumeSubHeadingListStart
\resumeSubheading
{1337 Coding School, UM6P}{Nov 2023 - Oct 2025}
{Software Engineer — Backend}{}
\resumeSubheading
{Faculty of Applied Sciences Ait Melloul, Ibn Zohr}{Sep 2021 - Jul 2023}
{Physics \& Chemistry}{}
\resumeSubHeadingListEnd

%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
\resumeSubHeadingListStart
\item{
  \textbf{Programming Languages}: Python, C, C++, Go, JavaScript, TypeScript, HTML5, CSS3, Bash
}
\item{
  \textbf{Frameworks \& Libraries}: ExpressJS, FastifyJS, PythonFlask
}
\item{
  \textbf{Databases \& ORM}: MongoDB, SQLite, Prisma
}
\item{
  \textbf{Tools \& DevOps}: Make, CMake, Git, Docker, Docker Compose, Nginx, Jest, Node, Bun
}
\resumeSubHeadingListEnd

\end{document}